Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-23 tsibbletalk.Rmd
start of shared data object

# Interactivity for coordinated views via shared temporal data

The \CRANpkg{tsibbletalk} package, inspired by the \CRANpkg{crosstalk} package, introduces a shared tsibble instance on top of a `tsibble` to allow for frictionless communication between different plots for temporal data. The `as_shared_tsibble()` function provides an entry point in the integrated flow, turning a `tsibble` to a shared instance (i.e. `SharedTsibbleData` subclassing of `SharedData` from \CRANpkg{crosstalk}) that powers data transmission across multiple views. The \CRANpkg{tsibbletalk} package aims to streamline interactive graphical analysis with the focus of temporal and structured linking.

@@

# Slicing and dicing time

>>>>

The techniques implemented in work described in this paper utilise web technology.

# Using a shared temporal data object for interactivity

The \CRANpkg{tsibbletalk} package introduces a shared tsibble instance built on a `tsibble`. This allows for seamless communication between different plots of temporal data. The `as_shared_tsibble()` function turns a `tsibble` into a shared instance,  `SharedTsibbleData`, which is a subclass of `SharedData` from \CRANpkg{crosstalk}). This is the object driving data transmission across multiple views. The \CRANpkg{tsibbletalk} package aims to streamline interactive exploration of temporal data, with the focus of temporal elements and structured linking.

## Linking between plots

@@

## Slicing and dicing time

### 2020-09-23 tsibbletalk.tex
start of shared data object

\hypertarget{interactivity-for-coordinated-views-via-shared-temporal-data}{%
\section{Interactivity for coordinated views via shared temporal
data}\label{interactivity-for-coordinated-views-via-shared-temporal-data}}

The \CRANpkg{tsibbletalk} package, inspired by the \CRANpkg{crosstalk}
package, introduces a shared tsibble instance on top of a
\texttt{tsibble} to allow for frictionless communication between
different plots for temporal data. The \texttt{as\_shared\_tsibble()}
function provides an entry point in the integrated flow, turning a
\texttt{tsibble} to a shared instance (i.e.~\texttt{SharedTsibbleData}
subclassing of \texttt{SharedData} from \CRANpkg{crosstalk}) that powers
data transmission across multiple views. The \CRANpkg{tsibbletalk}
package aims to streamline interactive graphical analysis with the focus
of temporal and structured linking.

@@

\hypertarget{slicing-and-dicing-time}{%
\section{Slicing and dicing time}\label{slicing-and-dicing-time}}

>>>>

The techniques implemented in work described in this paper utilise web
technology.

\hypertarget{using-a-shared-temporal-data-object-for-interactivity}{%
\section{Using a shared temporal data object for
interactivity}\label{using-a-shared-temporal-data-object-for-interactivity}}

The \CRANpkg{tsibbletalk} package introduces a shared tsibble instance
built on a \texttt{tsibble}. This allows for seamless communication
between different plots of temporal data. The
\texttt{as\_shared\_tsibble()} function turns a \texttt{tsibble} into a
shared instance, \texttt{SharedTsibbleData}, which is a subclass of
\texttt{SharedData} from \CRANpkg{crosstalk}). This is the object
driving data transmission across multiple views. The
\CRANpkg{tsibbletalk} package aims to streamline interactive exploration
of temporal data, with the focus of temporal elements and structured
linking.

\hypertarget{linking-between-plots}{%
\subsection{Linking between plots}\label{linking-between-plots}}

@@

\hypertarget{slicing-and-dicing-time}{%
\subsection{Slicing and dicing time}\label{slicing-and-dicing-time}}
